---
title: "Simple document"
output: 
html_document:
  toc: true
  toc_float: true
---

```{r}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:
#brackets around the r say that everything after it is r code 

```{r} 
samp = rnorm(100)
length(samp)
```

# Section 2: 

The quotes on the in-line are on the key next to the one, it's not an apostrophe.  An apostrophe won't work for the code. 

I can take the mean of the sample, too!
The mean is `r round(mean(samp), 2)`.

# Section 3

This is going to make a plot.  First I generate a dataframe, then use `ggplot` to make a scatterplot. Every time you knit a document, you start from scratch so you have to reload the library.  Put the library at the very beginning of the document to keep everything easy.  

You can name the chunks of code within the curly brackets with the r at the beginning of the code chunks. 

```{r chunk_scatterplot}
plot_df=
  tibble(
    x=rnorm(n=1000),
    y=1+2*x+rnorm(n=1000)
  )
```

#Section 4

Learning assessment: Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r learning_assessment1}

la_df = tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```

